---
title: "Introduction to dosefitr"
author: "Thiago Loreto Matos"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Introduction to dosefitr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  eval      = FALSE
)
```

## Overview

`dosefitr` provides an end-to-end dose-response analysis pipeline for two
assay types commonly used in drug discovery:

- **NanoBRET kinase binding assays** -- reads raw BMG PHERAstar plate-reader
  exports, computes BRET ratios, and derives IC50 / pIC50 values for kinase
  inhibitors.
- **Cell viability assays** -- reads luminescence or fluorescence plate-reader
  exports and fits dose-response curves to quantify compound cytotoxicity.

Both workflows share the same pipeline structure and downstream functions
(outlier removal, curve fitting, plotting, and Excel export), so switching
between assay types requires changing only one or two arguments.

### Pipeline overview

```
Raw Excel files
      |
      v
batch_ratio_analysis()        <- BRET: reads plates, computes BRET ratios
batch_viability_analysis()    <- Viability: reads plates, normalises signal
      |
      v
rout_outliers_batch()         <- detects and removes outliers  [optional]
      |
      v
batch_drc_analysis()          <- fits 3PL or 4PL dose-response curves
      |
      |---> batch_save_all_drc_plots()   <- one plot per compound
      |---> plot_multiple_compounds()    <- overlay selected compounds
      |---> compare_plates_drc()         <- compare compound across plates
      |---> scarab_table()              <- Scarab-format export (NanoBRET)
      `---> scarab_viability()          <- Scarab-format export (viability)
```

---

## Installation

```{r install}
# Install from GitHub
remotes::install_github("AKKDataAnalysis/dosefitr")
```

```{r load}
library(dosefitr)
```

---

## Input files

### Directory layout

All files for a single experiment should live in the same folder:

```
experiment_folder/
|-- info_tables.xlsx      <- metadata file (one sheet per plate)
|-- raw_data_1.xlsx       <- plate-reader export for plate 1
|-- raw_data_2.xlsx       <- plate-reader export for plate 2
`-- raw_data_3.xlsx       <- plate-reader export for plate 3
```

Each sheet in `info_tables.xlsx` is matched to a raw data file by the
trailing number in the filename (e.g. sheet `Plate_1` -> `raw_data_1.xlsx`).

### The metadata file (`info_tables.xlsx`)

This is the only file you need to create manually. It is an Excel workbook
with **one sheet per plate**. Each sheet must contain at least four columns
(column names can be anything; position matters):

| Position | Content | Example |
|---|---|---|
| 1 | Log10 inhibitor concentrations | `-9`, `-8.5`, `-8`, ... |
| 2 | Plate row letter(s) for this compound | `A`, `B`, `C`, ... |
| 3 | Construct / kinase name | `KinaseA`, `KinaseB` |
| 4 | Compound / inhibitor name | `CpdA`, `CpdB` |

A full 384-well plate (rows A-P) with one compound per row and three constructs.
The log(inhibitor) column lists the concentrations used in the experiment -- one
per row, in any order. These values are not tied to a specific plate row; the
function reads them as a sequence and assigns them to the data columns in order.

| log(inhibitor) | Plate_Row | Construct | Compound |
|---|---|---|---|
|  | A | KinaseA | CpdA |
| -4.61 | B | KinaseA | CpdB |
| -5.13 | C | KinaseA | CpdC |
| -5.61 | D | KinaseA | CpdD |
| -6.13 | E | KinaseA | CpdE |
| -6.61 | F | KinaseA | CpdF |
| -7.13 | G | KinaseA | CpdG |
| -7.61 | H | KinaseB | CpdH |
| -8.00 | I | KinaseB | CpdI |
| -8.43 | J | KinaseB | CpdJ |
| -8.91 | K | KinaseB | CpdK |
| -9.38 | L | KinaseC | CpdL |
|  | M | KinaseC | CpdM |
|  | N | KinaseC | CpdN |
|  | O | KinaseC | CpdO |
|  | P | KinaseC | CpdP |

> The log(inhibitor) column is a list of concentrations used in the experiment
> and is not tied to a specific plate row -- it is read as a sequence.

Columns 3 and 4 are combined as `Construct:Compound` (e.g. `KinaseA:CpdA`)
to label all output columns, plots, and export tables throughout the pipeline.

---

## Workflow 1 -- NanoBRET kinase binding assay

### Step 1: Process raw plates

`batch_ratio_analysis()` reads all PHERAstar Excel files in the working
directory, pairs them with the metadata file, computes BRET ratios
(acceptor / donor x 1000), and returns a named list with one entry per plate.

```{r nanobret-step1}
results <- batch_ratio_analysis(
  control_0perc       = 24,    # plate column for 0% control (e.g. DMSO)
  control_100perc     = 12,    # plate column for 100% control (e.g. staurosporine)
  output_dir          = "./qc_output",
  low_value_threshold = 1000,  # donor-channel values below this -> NA
  verbose             = TRUE
)
```

Wells where the donor-channel signal falls below `low_value_threshold` are
set to `NA` before the ratio is calculated, excluding failed or empty wells.

Column indices are the most common way to specify controls. Column names are
also accepted and must match the header row exactly as it appears in the file:

```{r nanobret-step1-colname}
results <- batch_ratio_analysis(
  control_0perc   = "DMSO",
  control_100perc = "Staurosporine",
  verbose         = TRUE
)
```

**Using duplicate 100% control columns (v2 mode):**

When the 100% control is measured in two columns that should be averaged, or
when the 0% control is a fixed instrument background value, use
`function_version = "v2"`:

```{r nanobret-step1-v2}
results <- batch_ratio_analysis(
  control_0perc       = 16,         # fixed background value
  control_100perc     = c(12, 24),  # two columns averaged into one
  low_value_threshold = 3000,
  function_version    = "v2",
  verbose             = TRUE
)
```

**Display separator in plots (`label_sep`):**

By default, construct and compound names are shown joined with `":"` in
plot titles and legends (e.g. `EPHA1:KK135`). To display them with a
different separator, pass `label_sep` to any plotting function:

```{r nanobret-step1-sep, eval=FALSE}
# Show "EPHA1/KK135" instead of "EPHA1:KK135" in legends and titles
plot_multiple_compounds(drc_results, label_sep = "/")
```

The internal data always uses `":"` — this parameter only affects how
labels appear in plots. It is available in `plot_multiple_compounds()`,
`batch_save_all_drc_plots()`, `compare_plates_drc()`, and
`plot_outliers_batch_curves()`.

**Consistent legend widths (`legend_width`):**

When generating multiple plots, legend widths can vary because shorter
labels produce narrower legends. The `legend_width` parameter in
`plot_multiple_compounds()` and `compare_plates_drc()` measures the rendered legend width in cm
and pads it to a target width via `legend.box.margin`, guaranteeing
the data panel is identically sized across plots.

- **Numeric target** pads the legend column to exactly this width (cm):

```{r legend-width, eval=FALSE}
plot_multiple_compounds(drc_results, legend_width = 4)
```

- **`"auto"` mode** measures and returns the current width without padding.
  Useful for determining the maximum across a set of plots:

```{r legend-width-auto, eval=FALSE}
p1 <- plot_multiple_compounds(drc_results, compound_indices = 1:5,
                              legend_width = "auto")
max_w <- attr(p1, "metadata")$legend_width_cm

# Then pad all plots to the maximum width
plot_multiple_compounds(drc_results, compound_indices = 1:5,
                        legend_width = max_w)
```

Only right- and left-positioned legends are affected. The measured width
is stored in `attr(p, "metadata")$legend_width_cm`.

### Step 2: Remove outliers (optional)

`rout_outliers_batch()` applies the ROUT method to each compound curve
independently. The `Q` parameter is the maximum acceptable false discovery
rate for outlier labelling (lower = more conservative).

The ROUT method is described in: Motulsky HJ & Brown RE, BMC Bioinformatics
2006, 7:123 (doi:10.1186/1471-2105-7-123).

```{r nanobret-step2}
results_clean <- rout_outliers_batch(
  batch_results     = results,
  Q                 = 0.01,      # 1% FDR -- recommended starting point
  n_param           = 4L,        # 4-parameter Hill model (free Hill slope)
  direction         = "inhibition",
  ntry_retry        = 3L,        # random restarts on non-convergence
  min_dynamic_range = 20,        # warn if dynamic range < 20%
  keep_cytotoxic    = FALSE,     # set TRUE for viability assays
  seed              = 42L,       # ensures reproducible outlier calls
  verbose           = TRUE
)

# Inspect flagged points
head(results_clean$outlier_summary)

# Visualise outlier-flagged curves
plot_outliers_batch_curves(results_clean)
```

`rout_outliers_batch()` overwrites `modified_ratio_table` in-place with the
cleaned data and preserves the original as `modified_ratio_table_original`.
Pass `results_clean` (not `results`) to `batch_drc_analysis()` to use the
cleaned data.

**Choosing `Q`:**

| `Q` value | Stringency | Use case |
|---|---|---|
| `0.001` | Very strict | High-confidence outlier removal only |
| `0.01` | Recommended | Standard NanoBRET and viability experiments |
| `0.05` | Lenient | Noisy assays or exploratory analysis |

Start with `Q = 0.01`. If biologically plausible points are being removed,
increase to `Q = 0.001`. If obvious outliers are being missed, decrease to
`Q = 0.05`.

### Step 3: Fit dose-response curves

`batch_drc_analysis()` fits a three-parameter logistic (3PL) model to each
compound curve and returns IC50, pIC50, R2, Hill slope, and confidence
intervals.

```{r nanobret-step3}
drc_results <- batch_drc_analysis(
  batch_results = results_clean,  # use results if you skipped Step 2
  normalize     = TRUE,
  output_dir    = "./drc_results",
  verbose       = TRUE
)
```

**3PL vs 4PL:**

- `model = "3pl"` (default): Hill slope fixed at -1. Recommended for standard
  sigmoidal inhibition curves with fewer free parameters.
- `model = "4pl"`: Hill slope freely estimated. Use when cooperative binding
  or mixed mechanisms are expected.

**Handling non-inhibitory curves:**

Flat curves (no meaningful response across the concentration range) always
have their IC50 and pIC50 reported as `"N/D"` (not determined). To also
suppress IC50 for activation curves (response increases with concentration):

```{r nanobret-step3-nd}
drc_results <- batch_drc_analysis(
  batch_results    = results_clean,
  normalize        = TRUE,
  nd_if_activation = TRUE   # activation curves -> N/D
)
```

**Accessing results:**

```{r nanobret-step3-access}
# Final summary table for plate 1 (IC50, pIC50, R2, Hill slope, ...)
summary_table <- drc_results$drc_results$plate_01$drc_result$final_summary_table

# Quality metrics table
quality_table <- drc_results$drc_results$plate_01$drc_result$curve_quality_table
```

### Step 4: Visualise results

**Save one plot per compound:**

```{r nanobret-step4-all}
batch_save_all_drc_plots(
  batch_drc_results    = drc_results,
  output_dir           = "DRC_Plots",
  verbose              = TRUE,
  y_axis_title         = NULL,          # auto-detects assay type
  y_limits             = NULL,          # NULL auto-scales; use c(0, 100) for fixed scale
  organize_by          = "plate",       # "plate" or "compound"
  format               = "png",
  width                = 10,
  height               = 10,
  dpi                  = 600,
  compounds_to_plot    = NULL,          # character vector to restrict compounds
  plates_to_plot       = NULL,          # character vector to restrict plates
  save_panel           = TRUE,          # also save a combined panel per plate
  panel_ncol           = 4L,
  panel_width_per_col  = 6,
  panel_height_per_row = 6,
  panel_spacing        = 1,
  subplot_title        = "auto"         # "auto", "compound", "construct", or fixed string
)
```

**Overlay selected compounds on one plot:**

```{r nanobret-step4-overlay}
# By index
plot_multiple_compounds(drc_results,
  plate            = "plate_01",
  compound_indices = 1:6,
  color_palette    = "colorblind",
  y_limits         = c(0, 100),   # or NULL to auto-scale to the data
  y_axis_title     = "Normalized BRET ratio [%]",
  show_error_bars  = TRUE,
  save_plot        = TRUE
)

# By name or partial match
plot_multiple_compounds(drc_results, target_compound = "KinaseA")

# Additional appearance controls
plot_multiple_compounds(drc_results,
  compound_indices       = 1:6,
  x_limits               = c(-9, -5),   # log10 molar; NULL auto-scales
  x_limits_scale         = "log10",      # "log10", "molar", "uM", or "nM"
  x_axis_title           = NULL,         # NULL uses default Log10 Concentration [M]
  curve_linewidth        = 1,
  curve_alpha            = 0.7,
  show_ic50_lines        = TRUE,         # dashed vertical line at each IC50
  plot_title_size        = 16,
  axis_line_color        = "black",
  show_border            = FALSE,
  transparent_background = FALSE
)
```

**Compare the same compound across plates:**

```{r nanobret-step4-compare}
compare_plates_drc(
  drc_results,
  compare_by    = "compound",
  color_palette = "set1",
  y_limits      = c(0, 100),   # or NULL to auto-scale to the data
  y_axis_title  = "Normalized BRET ratio [%]",
  min_plates    = 2,
  # Additional appearance controls (same as plot_multiple_compounds)
  x_limits               = NULL,
  show_ic50_lines        = FALSE,
  axis_line_color        = "black",
  show_border            = FALSE,
  transparent_background = FALSE,
  # Consistent legend widths across comparison plots
  legend_width           = NULL          # NULL = no padding; "auto" = two-pass measure + pad
)
```

**Consistent legend widths across plate comparison plots:**

When comparing plates, each plot's legend shows plate names. If plate names
have different lengths, the data panels will differ in width. Use
`legend_width = "auto"` to automatically measure all legends and pad to the
maximum — `compare_plates_drc()` handles the two-pass rendering internally:

```{r compare-legend-width, eval=FALSE}
compare_plates_drc(drc_results, legend_width = "auto")
```

### Step 5: Export results

**Generate a Scarab-format export table (NanoBRET):**

`scarab_table()` produces a 76-row Scarab-format data frame combining
experimental metadata, curve parameters, QC metrics, and raw BRET values.
The output is saved as an `.xlsx` file with two sheets: `Scarab_Table`
(fields as rows, compounds as columns) and `Scarab_Table_Transposed`
(compounds as rows -- easier for filtering in Excel).

```{r nanobret-step5-scarab}
scarab_table(
  results_list              = results,
  drc_results_list          = drc_results,
  plate_name                = "plate_01",
  date                      = "260323",
  experimenter_abbrev       = "TL",
  nLuc_orientation          = "C",       # "N" or "C" terminus
  tracer                    = "Tracer K10",
  tracer_kd_app             = -7.5,
  tracer_concentration_used = -7.5,
  decimal_separator         = ",",       # use "." for English format
  eubscarab_ready           = "No"
)
```

Per-kinase parameters (`nLuc_orientation`, `tracer`, `tracer_kd_app`,
`tracer_concentration_used`) accept a single value (applied to all kinases),
a named vector (keyed by kinase name), or an unnamed vector (applied in order
of unique kinases on the plate):

```{r nanobret-step5-scarab-multi}
scarab_table(
  results_list     = results,
  drc_results_list = drc_results,
  plate_name       = "plate_01",
  date             = "260323",
  experimenter_abbrev = "TL",
  nLuc_orientation = c(KinaseA = "C", KinaseB = "N"),
  tracer           = c(KinaseA = "Tracer K10", KinaseB = "Tracer 236"),
  tracer_kd_app    = c(KinaseA = -7.5, KinaseB = -8.0),
  tracer_concentration_used = c(KinaseA = -7.5, KinaseB = -8.0),
  decimal_separator = ","
)
```

---

## Workflow 2 -- Cell viability assay

The viability workflow is structurally identical to the NanoBRET workflow.
Replace `batch_ratio_analysis()` with `batch_viability_analysis()` in Step 1.
`batch_drc_analysis()` automatically detects the assay type from its input -- no extra parameter needed.
All other functions work without modification.

### Step 1: Process raw plates

```{r viability-step1}
via_results <- batch_viability_analysis(
  directory       = "data/viability/",
  control_0perc   = 1,    # column for background / vehicle control
  control_100perc = 24,   # column for untreated cells (maximum signal)
  output_dir      = "./qc_output",
  verbose         = TRUE
)
```

To exclude outer control columns from the compound data:

```{r viability-step1-cols}
via_results <- batch_viability_analysis(
  control_0perc    = 13,
  control_100perc  = 12,
  selected_columns = 2:23   # exclude columns 1 and 24
)
```

Per-plate quality metrics (CV%, Z-prime, signal-to-background) are computed
automatically and saved in the `Quality_Metrics` sheet of each per-plate
Excel file.

### Step 2: Remove outliers (optional)

Use `keep_cytotoxic = TRUE` to retain data points that resemble outliers but
are part of a genuine cytotoxic response (sharp drop at high concentrations):

```{r viability-step2}
results_clean <- rout_outliers_batch(via_results,
  Q              = 0.01,
  keep_cytotoxic = TRUE
)
```

### Step 3: Fit dose-response curves

```{r viability-step3}
drc_results <- batch_drc_analysis(
  batch_results = results_clean,  # use via_results if you skipped Step 2
  normalize     = TRUE,
  output_dir    = "./drc_results",
  verbose       = TRUE
)
```

### Step 4: Visualise and export

All plotting and export functions work identically to the NanoBRET workflow.
Pass a custom y-axis label where appropriate:

```{r viability-step4}
batch_save_all_drc_plots(drc_results,
  verbose      = TRUE,
  y_axis_title = "% Cell Survival",  # optional override; auto-detects "Cell Viability (%)" by default
  y_limits     = NULL   # NULL auto-scales each plot; use c(0, 100) for a fixed scale
)

plot_multiple_compounds(drc_results,
  compound_indices = 1:6,
  color_palette    = "colorblind",
  y_limits         = c(0, 100),   # or NULL to auto-scale to the data
  y_axis_title     = "% Cell Survival",  # optional override; auto-detects "Cell Viability (%)" by default
  save_plot        = TRUE
)

# Additional appearance controls (same as NanoBRET workflow)
plot_multiple_compounds(drc_results,
  compound_indices       = 1:6,
  x_limits               = c(-9, -5),   # log10 molar; NULL auto-scales
  x_limits_scale         = "log10",      # "log10", "molar", "uM", or "nM"
  x_axis_title           = NULL,
  curve_linewidth        = 1,
  curve_alpha            = 0.7,
  show_ic50_lines        = TRUE,
  plot_title_size        = 16,
  axis_line_color        = "black",
  show_border            = FALSE,
  transparent_background = FALSE
)
```

### Step 5: Export Scarab viability table

`scarab_viability()` generates a Scarab-format export for cell viability
experiments. It is the viability counterpart of `scarab_table()`.

```{r viability-step5}
scarab_viability(
  results_list        = via_results,
  drc_results_list    = drc_results,
  plate_name          = "plate_01",
  date                = "260323",
  experimenter_abbrev = "TL",
  cell_line           = "HeLa",
  cell_type           = "cervical adenocarcinoma",
  treatment_time      = "72h",
  measurement_method  = "CellTiter-Glo",
  assay_volume        = "40",
  plate_format        = "384-well",
  decimal_separator   = ","   # use "." for English format
)
```

The output is saved as an `.xlsx` file with two sheets: `Scarab_Table`
(fields as rows, compounds as columns) and `Scarab_Table_Transposed`
(compounds as rows -- easier for filtering in Excel).

---

## Merging replicate plates (optional)

When the same experiment is run across multiple plates (biological
replicates), `merge_plate_replicates()` combines their data tables into a
single entry that feeds directly into all downstream functions.

```{r merge}
# Merge all plates
merged <- merge_plate_replicates(results)

# Merge a subset, keeping others separate
merged <- merge_plate_replicates(results,
  plates      = c("plate_01", "plate_02"),
  merged_name = "rep1_rep2"
)

# Save the Excel report to a custom directory (default: drc_quality/ in working dir)
merged <- merge_plate_replicates(results, output_dir = "./my_reports")

# Feed into the DRC step as usual
drc_results <- batch_drc_analysis(
  batch_results = merged,
  normalize     = TRUE,
  output_dir    = "./drc_results"
)
```

Replicate columns are renumbered sequentially across plates
(`KinaseA:CpdA`, `KinaseA:CpdA.2` from plate 1 become
`KinaseA:CpdA.3`, `KinaseA:CpdA.4` from plate 2, and so on).
Compounds that appear in only some plates are included with however many
replicates they have -- no NA-padding is added.

---

## Complete example -- NanoBRET

```{r full-nanobret}
library(dosefitr)

setwd("path/to/experiment")

# 1. Process raw plates
results <- batch_ratio_analysis(
  control_0perc       = 24,
  control_100perc     = 12,
  output_dir          = "./qc_output",
  low_value_threshold = 1000,
  verbose             = TRUE
)

# 2. Remove outliers
results_clean <- rout_outliers_batch(results, Q = 0.01)
plot_outliers_batch_curves(results_clean)

# 3. Fit dose-response curves
drc_results <- batch_drc_analysis(
  batch_results = results_clean,
  normalize     = TRUE,
  output_dir    = "./drc_results",
  verbose       = TRUE
)

# 4. Save all individual plots
batch_save_all_drc_plots(drc_results, verbose = TRUE)

# 5. Overlay selected compounds
plot_multiple_compounds(drc_results,
  plate            = "plate_01",
  compound_indices = 1:6,
  color_palette    = "colorblind",
  y_limits         = c(0, 100),   # or NULL to auto-scale
  y_axis_title     = "Normalized BRET ratio [%]",
  save_plot        = TRUE
)

# 6. Compare the same compound across plates
compare_plates_drc(drc_results, compare_by = "compound")

# 7. Export Scarab table
scarab_table(
  results_list              = results,
  drc_results_list          = drc_results,
  plate_name                = "plate_01",
  date                      = "260323",
  experimenter_abbrev       = "TL",
  nLuc_orientation          = "C",
  tracer                    = "Tracer K10",
  tracer_kd_app             = -7.5,
  tracer_concentration_used = -7.5,
  decimal_separator         = ",",
  eubscarab_ready           = "No"
)
```

---

## Complete example -- Cell viability

```{r full-viability}
library(dosefitr)

setwd("path/to/experiment")

# 1. Process raw plates
via_results <- batch_viability_analysis(
  control_0perc    = 13,
  control_100perc  = 12,
  selected_columns = 2:23,
  verbose          = TRUE
)

# 2. Remove outliers (keep cytotoxic points)
results_clean <- rout_outliers_batch(via_results,
  Q              = 0.01,
  keep_cytotoxic = TRUE
)
plot_outliers_batch_curves(results_clean)

# 3. Fit dose-response curves
drc_results <- batch_drc_analysis(
  batch_results = results_clean,
  normalize     = TRUE,
  output_dir    = "./drc_results",
  verbose       = TRUE
)

# 4. Save all individual plots
batch_save_all_drc_plots(drc_results,
  verbose      = TRUE,
  y_axis_title = "% Cell Survival"  # optional override; auto-detects "Cell Viability (%)" by default
)

# 5. Overlay selected compounds
plot_multiple_compounds(drc_results,
  compound_indices = 1:6,
  color_palette    = "colorblind",
  y_limits         = c(0, 100),   # or NULL to auto-scale
  y_axis_title     = "% Cell Survival",  # optional override; auto-detects "Cell Viability (%)" by default
  save_plot        = TRUE
)

# 6. Export Scarab viability table
scarab_viability(
  results_list        = via_results,
  drc_results_list    = drc_results,
  plate_name          = "plate_01",
  date                = "260323",
  experimenter_abbrev = "TL",
  cell_line           = "HeLa",
  treatment_time      = "72h",
  measurement_method  = "CellTiter-Glo",
  decimal_separator   = ","
)
```

---

## Single-plate workflow

For interactive exploration or when you have a single plate, use the
lower-level functions directly instead of the batch pipeline.

```{r single-plate-ratio}
# Load a single raw data frame
raw_data  <- readxl::read_excel("NanoBRET_plate_1.xlsx", sheet = 1, col_names = FALSE)
info      <- readxl::read_excel("info_tables.xlsx", sheet = "Sheet1")

# Compute BRET ratios for one plate
plate_result <- ratio_dose_response_v2(
  data             = raw_data,
  control_0perc    = 16,
  control_100perc  = c(12, 24),
  info_table       = info,
  split_replicates = TRUE,
  verbose          = TRUE
)

# Detect outliers for one plate
plate_clean <- rout_outliers(
  data      = plate_result$modified_ratio_table,
  Q         = 0.01,
  seed      = 42L
)

# Visualise outlier-flagged curves for one plate
plot_outliers_curves(
  rout_output = plate_clean,
  title       = "Plate 1"
)
```

For viability data, replace `ratio_dose_response_v2()` with
`process_viability_data()`:

```{r single-plate-viability}
raw_via  <- readxl::read_excel("viability_plate_1.xlsx", sheet = 1, col_names = FALSE)
info_via <- readxl::read_excel("info_tables.xlsx", sheet = "Sheet1")

plate_via <- process_viability_data(
  data             = raw_via,
  control_0perc    = 1,
  control_100perc  = 24,
  info_table       = info_via,
  split_replicates = TRUE,
  verbose          = TRUE
)
```

To plot a single fitted dose-response curve from `fit_drc_3pl()` or
`fit_drc_4pl()` output, use `plot_dose_response()`:

```{r single-plate-plot}
# Fit a single plate
fit <- fit_drc_3pl(data = plate_clean$cleaned_table, normalize = TRUE)

# Plot compound 1
plot_dose_response(
  results        = fit,
  compound_index = 1,
  y_limits       = c(0, 120),
  x_limits       = c(-9, -5),     # log10 molar; NULL auto-scales
  show_ic50_line = TRUE,
  save_plot      = "compound1_curve.png"
)
```

---

## Function reference

### Batch pipeline functions

| Function | Description |
|---|---|
| `batch_ratio_analysis()` | Read raw NanoBRET plates, compute BRET ratios |
| `batch_viability_analysis()` | Read raw viability plates, normalise signal |
| `merge_plate_replicates()` | Merge replicate plates into a single combined result |
| `rout_outliers_batch()` | ROUT outlier detection across all plates |
| `plot_outliers_batch_curves()` | Visualise outlier-flagged curves (batch) |
| `batch_drc_analysis()` | Fit 3PL or 4PL dose-response curves across all plates |
| `batch_save_all_drc_plots()` | Save one plot per compound across all plates |
| `plot_all_dose_responses()` | Save individual dose-response plots from a single-plate result |
| `plot_multiple_compounds()` | Overlay selected compounds on one plot |
| `plot_drc_batch()` | Overlay compounds across plates with faceting support |
| `compare_plates_drc()` | Compare the same compound across plates |
| `scarab_table()` | Generate Scarab-format export table (NanoBRET) |
| `scarab_viability()` | Generate Scarab-format export table (cell viability) |

### Single-plate / lower-level functions

| Function | Description |
|---|---|
| `ratio_dose_response()` | Compute BRET ratios for a single plate (v1 engine) |
| `ratio_dose_response_v2()` | Compute BRET ratios for a single plate (v2 engine) |
| `process_viability_data()` | Normalise viability signal for a single plate |
| `fit_drc_3pl()` | Fit a single plate with a 3-parameter logistic model |
| `fit_drc_4pl()` | Fit a single plate with a 4-parameter logistic model |
| `plot_dose_response()` | Plot a single dose-response curve |
| `rout_outliers()` | ROUT outlier detection for a single plate |
| `plot_outliers_curves()` | Visualise outlier-flagged curves for a single plate |

### Utility functions

| Function | Description |
|---|---|
| `reshape_dr_table()` | Reshape dose-response results to standardised publication format |
| `save_multiple_sheets()` | Export multiple data frames to a formatted Excel file |
